An elaborate data set on human gait and the effect of mechanical perturbations

### 2015-06-08 paper.tex
Fixed typo R-Link > R-Mill.

Early on, we discovered that the factory setup of the R-Link treadmill had a
vibration mode as low as 5\si{\hertz} that was detectable in the force
measurements; likely due to the flexible undercarriage and pitch motion
mechanism. Trials 6--8 are affected by this vibration mode. During trials 9--15
the treadmill was stabilized with wooden blocks. During the remaining trials
($>$~15) the treadmill was stabilized with metal supports; both with ones we
fabricated in-house and ones supplied by the vendor. These supports aimed to
improve the stiffness and frequency response of the force plate system. See the
Data Limitations Section for more details.

>>>>

Early on, we discovered that the factory setup of the R-Mill treadmill had a
vibration mode as low as 5\si{\hertz} that was detectable in the force
measurements; likely due to the flexible undercarriage and pitch motion
mechanism. Trials 6--8 are affected by this vibration mode. During trials 9--15
the treadmill was stabilized with wooden blocks. During the remaining trials
($>$~15) the treadmill was stabilized with metal supports; both with ones we
fabricated in-house and ones supplied by the vendor. These supports aimed to
improve the stiffness and frequency response of the force plate system. See the
Data Limitations Section for more details.
